Word-Referent Identification Under Multimodal Uncertainty

### 2018-04-26 Writeup/ms.tex
modif ms

\noindent The descriptive model explained 95\% of total variance.
However, since the descriptive model was fit to the same data, there is
a risk that this high correlation is due to overfitting. To examine this
possibility, we cross-validated the model using half the responses to
predict the other half (averaging across 10 random partitions). The
predictive power of the model remained very high (\(r^2\)=0.93).

@@

As a second analysis, we asked whether the observed variance in the
individual distribution was due to mere sampling errors or whether it
corresponded to a real between-subject variability. We simulated
individual responses from the posterior distribution whose parameters
were fit to the population as a whole (i.e., the descriptive posterior).
The resulting distribution is shown in Figure~\ref{fig:individual}. For
ease of comparison, the simulated distribution was superimposed to the
real distribution. We found that the real distribution had a standard
deviation of \(sd=\) 2.24 which was larger than that of the simulated
distribution (\(sd=\) 1.10), indicating that there was real
between-subject variation beyond sampling errors. This finding means
that the participants varied in terms of how they weighted modalities:
Compared to the predictions of the population-level model, some
participants relied more on the auditory modality, whereas others relied
more on the visual modality.

@@

This work studied the mechanism of spoken word identification under
uncertainty in both the form and the referent. We conducted an ideal
observer analysis of this task. We found people to be near optimal in
their cue combination (at least at the population level): They weighted
each modality according to its relative reliability. However, they also
showed patterns of sub-optimality especially when the stimuli were
perturbed with additional background noise. This work provides a formal
framework where old and new questions about word recognition in a
referential context can be given a precise formulation. For instance, of
particular interest is the case of iconicity, that is, when there is a
resemblance between the sound of a word and its referent. Previous work
has suggested that iconicity, among other things, helps with learning
(and generalizing the meaning of) new words (see Dingemanse, Blasi,
Lupyan, Christiansen, \& Monaghan, 2015 for a review). Using the
research strategy in this paper, we can, for example, test whether
iconicity has such an advantage becuase it mitigates the sub-optimal
patterns observed with more arbitrary pairings. Finally, though the
current framework only characterizes adult word recognition, it provides
a first step towards a model where developmental questions can also be
investigated. For instance, future work should explore whether children,
like adults, use probabilistic cues from both the auditory and the
visual input to recognize ambiguous words, the extent to which they
combine these cues in an optimal fashion, and whether these combination
help them with refining their early phonological and semantic
representations.

>>>>

\noindent The descriptive model explained 95\% of total variance.
However, since the descriptive model was fit to the same data, there is
a risk that this high correlation is due to overfitting. To examine this
possibility, we cross-validated the model using half the responses to
predict the other half (averaging across 10 random partitions). The
predictive power of the model remained very high (\(r^2\)=0.92).

@@

As a second analysis, we asked whether the observed variance in the
individual distribution was due to mere sampling errors or whether it
corresponded to a real between-subject variability. We simulated
individual responses from the posterior distribution whose parameters
were fit to the population as a whole (i.e., the descriptive posterior).
The resulting distribution is shown in Figure~\ref{fig:individual}. For
ease of comparison, the simulated distribution was superimposed to the
real distribution. We found that the real distribution had a standard
deviation of \(sd=\) 2.24 which was larger than that of the simulated
distribution (\(sd=\) 1.15), indicating that there was real
between-subject variation beyond sampling errors. This finding means
that the participants varied in terms of how they weighted modalities:
Compared to the predictions of the population-level model, some
participants relied more on the auditory modality, whereas others relied
more on the visual modality.

@@

This work studied the mechanism of spoken word identification under
uncertainty in both the form and the referent. We conducted an ideal
observer analysis of this task. We found people to be near optimal in
their cue combination (at least at the population level): They weighted
each modality according to its relative reliability. However, they also
showed patterns of sub-optimality especially when the stimuli were
perturbed with additional background noise. This work provides a formal
framework where old and new questions about word recognition in a
referential context can be given a precise formulation. For instance, of
particular interest is the case of iconicity, that is, when there is a
resemblance between the sound of a word and its referent. Previous work
has suggested that iconicity, among other things, helps with learning
(and generalizing the meaning of) new words (see Dingemanse, Blasi,
Lupyan, Christiansen, \& Monaghan, 2015 for a review). Using the
research strategy in this paper, we can, for example, test whether
iconicity has such an advantage because it mitigates the sub-optimal
patterns observed with more arbitrary pairings. Finally, though the
current framework only characterizes adult word recognition, it provides
a first step towards a model where developmental questions can also be
investigated. For instance, future work should explore whether children,
like adults, use probabilistic cues from both the auditory and the
visual input to recognize ambiguous words, the extent to which they
combine these cues in an optimal fashion, and whether these combination
help them with refining their early phonological and semantic
representations.
